Certified Desugaring of Javascript Programs using Coq

### 2016-12-14 paper/paper.tex
Added subsection on precomputed inversion.

At this stage we stumbled upon an interesting performance issue 
involving the Coq proof assistant. The proof of completeness required
inverting the pretty-big-step semantics judgment; this turned out
to be very slow, and also generated large proof terms, which increased
the memory footprint. The problem is well-known~\cite{Monin:Coq2}; 
our solution involved
precomputing the required inversion principles using
\texttt{Derive Inversion}, and using the precomputed inversion
principles to create a specialized inversion tactic.

\asi{Put a forward pointer to a section where we described the issue in more
  details.}

@@

>>>>

% This was moved.
%At this stage we stumbled upon an interesting performance issue 
%involving the Coq proof assistant. The proof of completeness required
%inverting the pretty-big-step semantics judgment; this turned out
%to be very slow, and also generated large proof terms, which increased
%the memory footprint. The problem is well-known~\cite{Monin:Coq2}; 
5our solution involved
%precomputing the required inversion principles using
%\texttt{Derive Inversion}, and using the precomputed inversion
%principles to create a specialized inversion tactic.

%\asi{Put a forward pointer to a section where we described the issue in more
%  details.}

@@

\subsection{Precomputed inversion}

Developing the correctness proof for the JavaScript desugaring required
inverting the \lambdajs pretty-big-step semantics judgment; this
turned out to be very slow, and also generated large proof terms, which 
increased the memory footprint. The problem is well-known~\cite{Monin:Coq2}.
To solve it, we precomputed the required inversion principles
using \texttt{Derive Inversion}, e.g.:
\begin{minted}{coq}
Derive Inversion inv_red_exprh_if with (forall k c st e e1 e2 oo,
    red_exprh k c st (expr_if e e1 e2) oo) Sort Prop.
\end{minted}
Using these, we created a specialized inversion tactic
which selects and applies the required induction principle.
The \texttt{Derive Inversion} calls and the tactic definitions
are generated automatically from the Coq definition of the semantics.

Unfortunately, this technique was still not efficient enough to be
applied to JSCert: the definition of the JavaScript semantics in
JSCert has around 10 times more semantic rules than the definition
in \lambdajs.

\subsection{Proof automation}
